Hector Permafrost

### 2019-05-30 analysis/paper/paper.Rmd
Set up paper deployment on gh-pages
Add true HTML export (including MathJax)

---
title: "Hector Permafrost"
author:
  - Alexey N. Shiklomanov
  - Ben Bond-Lamberty
  - Ben Kravitz?
  - Kate Calvin?
  - Corinne Hartin
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx"
bibliography: ["references.bib", "packages.bib"]
csl: "../templates/biogeosciences.csl"
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)

>>>>

---
title: "Hector Permafrost"
author:
  - Alexey N. Shiklomanov
  - Ben Bond-Lamberty
  - Ben Kravitz?
  - Kate Calvin?
  - Corinne Hartin
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx"
    rmarkdown::github_document:
      html_preview: false
bibliography: ["references.bib", "packages.bib"]
csl: "../templates/biogeosciences.csl"
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>"
)
